Our Title

### 2015-05-08 draft.tex
Merged in "Land" and "Finances" subsections in the Introduction chapter.

@@

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.6]{./figures/current_territory.png}
   \caption{Current ISIL Territory}
     \label{fig:current_territory}
\end{figure}

>>>>

ISIL controls land in Iraq and Syria, including several cities that include Arbil and Mosul in Iraq and Aleppo and Raqqa in Syria \cite{McFate2015}.  Iraqi military forces, supported by U.S. airstrikes, have recently pushed ISIL out of Tikrit in Northern Iraq, and are now gearing up to push ISIL out of various location in Anbar province, including Falluja and Ramadi \cite{Nordland2015}.  In April 2015, the Pentagon released an assessment that Iraqi forces had pushed ISIL out of roughly 25\% of the territory it had seized in advances during 2014 - an area that represents between 5,000 and 6,500 square miles \cite{Michaels2015}.  ISIL's territory is pictured in \autoref{fig:current_territory2}, with indications of the areas in which ISIL territory has been rolled back in the first several months of 2015.

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.6]{./figures/current_territory.png}
   \caption{Current ISIL Territory \cite{BBC2015a}}
     \label{fig:current_territory2}
\end{figure}

@@

ISIL has a number of key sources of income, which may be categorized into five key groups, listed in order of magnitude \cite{Report2015}:

\begin{itemize}
\item \textbf{Illicit proceeds from occupation of territory, including oil, extortion, and bank looting:} ISIL's sophisticated extortion racket is similar to that of organized crime rings. ISIL uses force to gain and control resources, including banks, oil and phosphates, agriculture, and archeological sites \cite{Report2015}.
\item \textbf{Kidnapping for ransom:} Reports indicate that ISIL has kidnapping hundreds of people, including Iraqis, Syrians, local ethnic minorities, Westerners, and East Asians. While ISILs murdering of hostages was garnered widespread attention, they have also been effective in extracting ransom payments, with revenue estimated between \$20 million and \$45 million USD \cite{Report2015}.
\item \textbf{Donations:} While revenue from external donations has been a relatively small portion of ISIL's income, it has recently been growing in importance. In addition to donations from the Gulf, there is also risk that wire transfers to charitable foundations operating in ISIL territory end up in ISIL's hands \cite{Report2015}. 
\item \textbf{Material support from foreign fighters:} In some instances, foreign terrorist fighters collect money in their home countries and uses it to provide monetary support to ISIL \cite{Report2015}.
\item \textbf{Online fundraising:} While fundraising through modern communications networks is a relatively small  piece of ISIL's income, the group has shown a strong ability to use social media sites such as Twitter and online crowd funding to support its operations \cite{Report2015}.
\end{itemize}

ISIL's operations have been largely self-sustaining, relying on oil income and other criminal and terrorist activities that generated millions of dollars per month \cite{TheWallStreetJournal2014}.  However, recent reports indicate that U.S. Operation Inherent Resolve has disrupted ISIL income streams considerably. The Pentagon reported in early February 2015 that ISIL's main source of income is no longer oil \cite{AlArabiyaNews2015}.  Pentagon spokesperson Rear Admiral John Kirby told reporters during press briefing that following months of airstrikes in the territory it controls, ISIL's oil income was being degraded, and that the group's primary source of income had shifted to donations and trade on black markets \cite{AlArabiyaNews2015}.

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.6]{./figures/current_territory.png}
   \caption{Current ISIL Territory \cite{BBC2015a}}
     \label{fig:current_territory}
\end{figure}
